---
title: "Lab 8"
author: "Van Gonzales"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(here)
library(broom)
```

### Read in data
```{r}
homes <- read_csv(here("slo_homes.csv"))
```

### Create a subset for 4 cities

Task: create a subset (called homes_subset) that only contains observations where the city is:
- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Sanata Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price))

# Include eval = false in the setup chunk if you dont want it to show up or even run everytime but you want to hang on to the code
```


Task: Explore the relationship between sqft and price in a scatterplot

```{r}
  ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")

# looks like it follows a positive correlation between sq ft and prices
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Creeat two diff permutations of the model

(1) price ~ city, berooms, bathrooms, sqft, status
(2) price ~ city,sqft, status
(3) try another one

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)
lm3 <- lm(Price ~ Bedrooms + Status, data = homes_subset)

lm1
# city reference level is Arroyo Grande
lm2
lm3
  
summary(lm1)
summary(lm2)
# 53% of the variance in home price is explained by the model
```

```{r}
# if i want SLO to be the ref level:
# ues fct_relevel to specify a new level

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo")
```

```{r}
lm4 <-lm(Price ~ City + Status, data = new_homes_subset)
```

### Explore correlations between quantitative variables

Task: make a subset called homes_quant that only contains the variables Price through SqFt

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```

### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)

# lower AIC means better fit
```

### Use model summary to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### check out diagnostic plots for lm1

```{r}
plot(lm1)
```

### use broom::augment() to return the predictions for existing observations
```{r}
home_predictions <- augment(lm1)
```

# make a histogram of the residuals from this model

```{r}
ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

